% !TEX TS-program = xelatex
% !TEX encoding = UTF-8



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% INSTRUCTIONS FOR COMPILING THIS DOCUMENT ("CV.tex")
%% TeX ---(XeLaTeX)---> PDF:
%%
%% Method 1: Use latexmk for fully automated document generation:
%%   latexmk -xelatex "CV.tex"
%%   (add the -pvc switch to automatically recompile on changes)
%%
%% Method 2: Use XeLaTeX directly:
%%   xelatex "CV.tex"
%%   (run multiple times to resolve cross-references if needed)
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% \documentclass[a4paper,10pt,oneside]{article}
\documentclass[letterpaper,10pt,oneside]{article}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% TYPESETTING OPTIONS.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\TypesetInNonStopMode}{1}
\newcommand{\TypesetInDraftMode}{0}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% PREAMBLE.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\input{CV-Preamble.tex}

% CV Info (to be customized).
\newcommand{\CVAuthor}{Raghav Toshniwal}
\newcommand{\CVTitle}{CV}
\newcommand{\CVNote}{Compiled using {\LaTeX}}
\newcommand{\CVWebpage}{http://raghav.website}

% PDF settings and properties.
\hypersetup{
pdftitle={\CVTitle},
pdfauthor={\CVAuthor},
pdfsubject={\CVWebpage},
pdfcreator={XeLaTeX},
pdfproducer={},
pdfkeywords={},
pdfpagemode={},
bookmarks=true,
unicode=true,
bookmarksopen=true,
pdfstartview=FitH,
pdfpagelayout=OneColumn,
pdfpagemode=UseOutlines,
hidelinks,
breaklinks}

% Shorthand.
\newcommand{\CodeCommand}[1]{\mbox{\textbf{\textbackslash{#1}}}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% ACTUAL DOCUMENT.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%%%%%%%%%%%%%%%
% TITLE BLOCK %
%%%%%%%%%%%%%%%

\title{\CVAuthor}

\begin{subtitle}
{8a, Northumberland Avenue, London WC2N 5BY, United Kingdom}
\par
\href{mailto:raghav.toshniwal@gmail.com}
{raghav.toshniwal@gmail.com}
\,\SubBulletSymbol\,
+44\,7521\,425-914
\,\SubBulletSymbol\,
\href{\CVWebpage}
{raghav.website}
\end{subtitle}

\begin{body}

%%%%%%%%%%%%%%%
%% EDUCATION %%
%%%%%%%%%%%%%%%

\section
{Education}
{Education}
{PDF:Education}

{\textbf{London School of Economics and Political Science}},
London, United Kingdom

\GapNoBreak
\BulletItem
MSc in
{Management of Information Systems and Digital Innovation}
\hfill
\DatestampYMD{2015}{0}{0} --
\DatestampYMD{2016}{0}{0}
\begin{detail}
\SubBulletItem
Courses Taken:
{Data Governance and Privacy, Innovating Organisation IT, Big Data and Social Computing}
\SubBulletItem
Research areas:
Application Programming Interfaces, Privacy by Design
\end{detail}
\BigGap
{\textbf{St Xavier's College}},
Kolkata, India

\GapNoBreak
\BulletItem
BSc in
{Computer Science (Hons)}
\hfill
\DatestampYMD{2012}{0}{0} --
\DatestampYMD{2015}{0}{0}
\begin{detail}
\SubBulletItem
Thesis:
{Design of an Intelligent Voice Controlled Home Automation System}
\SubBulletItem
Courses Taken:
Algorithms and Data structures, Compiler Theory, Operating System, Database Management
\SubBulletItem
Minor:
Mathematics and Physics
\SubBulletItem
Grade obtained:
First.
\end{detail}


\BigGap
{\textbf{St. James' School}},
Kolkata India

\GapNoBreak
\BulletItem
Indian School Certificate
\hfill
\DatestampYMD{2012}{0}{0}
\begin{detail}
\SubBulletItem
Overall Aggregate: 94.3\%
\SubBulletItem
Computer Science: 97\%
\end{detail}

%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% WORK EXPERIENCE %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section
{Work\newline
Experience}
{Other Work Experience}
{PDF:OtherWorkExperience}


{\textbf{Make A Difference}}


\GapNoBreak
\BulletItem
Mentor \& Teacher
\hfill
\DatestampYMD{2012}{0}{0} --
\DatestampYMD{2015}{0}{0}
\begin{detail}
\SubBulletItem
Taught Mathematics, English and Computer Science to underprivileged children in a shelter home.
\SubBulletItem
Mentored a group of 12 Volunteers who were part of an NGO and aided them with their work.
\SubBulletItem
Achieved highest city wide volunteer efficiency and lowest volunteer attrition rates.
\end{detail}
\BigGap

{\textbf{Blacklanche}}


\GapNoBreak
\BulletItem
Founder
\hfill
\DatestampYMD{2011}{0}{0} --
\DatestampYMD{2015}{0}{0}
\begin{detail}
\SubBulletItem
Ran a software development startup specializing in web and mobile application development.
\SubBulletItem
Received exemplary client feedback for high quality work and attention to detail.
\end{detail}

%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Notable Projects %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section
{Personal\newline
Projects}
{Other Work Experience}
{PDF:OtherWorkExperience}


{\textbf{Commeta}}
\hfill
\DatestampYMD{2016}{0}{0}
\begin{detail}
A browser-extension, built using Flask, allowing users to comment on any website. \newline Users do not have to register with any website or adhere to any moderation. It can even be used with websites that do not allow comments. 
\end{detail}

\GapNoBreak
{\textbf{Wiki Bacon}}
\hfill
\DatestampYMD{2016}{0}{0}
\begin{detail}
A web-service that calculates the shortest path using links from any Wikipedia article to a particular article. \newline It was built to explore the network properties of Wikipedia as a Scale Free Network.
\newline
It got featured on the Show page of Hacker News.
\newline
\href{http://wikibacon.pancakeapps.com}{Visit: http://wikibacon.pancakeapps.com}
\end{detail}

\GapNoBreak
{\textbf{Farket}}
\hfill
\DatestampYMD{2015}{0}{0}
\begin{detail}
An Internet based farmer's market using text messages for interfacing. It allows farmers to negotiate rates leveraging the ubiquity of the Internet. 
\newline
Ideal for rural areas with low Internet penetration.
\newline
\href{http://raghav.website/farket}{Read more at: http://raghav.website/farket}
\end{detail}

\GapNoBreak


%%%%%%%%%%%%%%%%%%
%% PUBLICATIONS %%
%%%%%%%%%%%%%%%%%%

\section
{Publications}
{Publications}
{PDF:Publications}

\subsection
{Journals}
{Journals}
{PDF:Journals}

\GapNoBreak

{\underline{R.~Toshniwal}, A.~Nath, and K.~Dastidar,
``Big Data Security Issues and Challenges,''
\textit{International Journal of Innovative Research in Advanced Engineering },
vol.~2,
no.~2,
\DatestampYM{2015}{02}.}

% Note the use of {\CharSpace} for aligning shorter numbers.
\Gap

{\underline{R.~Toshniwal} , S.~Chakrabarty, and R.~Beed,
``Solar-Powered Automated Plant/Crop Watering
System,''
\textit{International Journal of Advanced Engineering and Global Technology },
vol.~3,
no.~1,
\DatestampYM{2015}{1}.}


%%%%%%%%%%%%%%%%%%%%%
%% ACADEMIC AWARDS %%
%%%%%%%%%%%%%%%%%%%%%

\section
{Awards and \newline Achievements}
{Awards and \newline Achievements}
{PDF:AcademicAwards}

\BulletItem
Summa cum laude,
St. Xavier's College.
\hfill
\DatestampY{2015}
\BulletItem
Assistant Secretary,
Xavier’s Quizzing and Debating and Society
\hfill
\DatestampY{2015}
\BulletItem
Microsoft Best Cloud Hack,
Imperial College Hackathon
\hfill
\DatestampYM{2016}{02}
%%%%%%%%%%%%
%% SKILLS %%
%%%%%%%%%%%%

\section
{Skills}
{Skills}
{PDF:Skills}
Java,
Python,
C,
Mobile Application Development (iOS and Android),
AngularJS,
MySQL,
HTML, Javascript, CSS
{\LaTeX},
Adobe Photoshop,
Microsoft Office.


\begin{flushright}
\UseNoteFont%
[\textit{\CVNote}]%
\hspace{1.0mm}\null
\end{flushright}
\end{body}
\end{document}
